---
title: "Homework 6 - lvr2115"
author: "Laura Robles-Torres"
date: "2023-11-30"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages, message=FALSE}
library(modelr)
library(tidyverse)
library(mgcv)
library(p8105.datasets)

set.seed(1)
```

# Problem 2

```{r import data, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

This code creates a multiple linear regression model with 'tmax' as the response with 'tmin' and 'prcp' as the predictors. 

```{r}
fit = lm(tmax ~ tmin + prcp, data = weather_df)

fit |> 
  broom::glance()

fit |>
  broom::tidy()
```

```{r dist of r squared with plot}
#bootstrapping
weather_r2 = 
  weather_df |> 
    modelr::bootstrap(n = 500, id="strap_number") |> 
    mutate(
     models = map(.x=strap, ~lm(tmax ~ tmin + prcp, data = .x)),
     results = map(.x=models, broom::glance)) |> 
    select(strap_number, results) |>
    unnest(results) 

#plot
weather_r2 |> 
  ggplot(aes(x = r.squared)) + geom_density()

#confidence intervals
weather_r2|>
  summarize(
    ci_lower = quantile(r.squared, 0.025), 
    ci_upper = quantile(r.squared, 0.975))
```

```{r dist of log of b1*b2 with plot}
#bootstrapping
weather_log =
  weather_df |> 
    modelr::bootstrap(n = 500, id="strap_number") |> 
     mutate(
      models = map(.x=strap, ~lm(tmax ~ tmin + prcp, data = .x)),
      results = map(.x=models, broom::tidy))|>
    select(strap_number, results) |>
    unnest(results) |>
    pivot_wider(
      names_from = term, 
      values_from = estimate) |>
    group_by(strap_number) |>
    summarize(
     log_product=log(tmin*prcp)
    )

#plot
weather_log |>
  ggplot(aes(x=log_product))+geom_density()

#confidence intervals 
weather_log|>
  summarize(
    ci_lower = quantile(log_product, 0.025), 
    ci_upper = quantile(log_product, 0.975))
```

# Problem 3

```{r import and clean data, message=FALSE}
birthweight = 
  read_csv("./birthweight.csv") |>
  janitor::clean_names(case="snake") |>
  drop_na() |>
  mutate(
    id = row_number(),
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace))
```

## Proposing a model

### Full model
```{r full model}
fit = lm(bwt ~ ., data = birthweight)
         
fit |>
  broom::tidy() |>
  select(term, estimate, p.value) |> 
  knitr::kable(digits = 3)

```

### Plot model residuals vs. fitted values

```{r}
birthweight |> 
  add_predictions(fit) |>
  add_residuals(fit) |>
  ggplot(aes(x = pred, y = resid)) +  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "Residuals vs Fitted Values ")
```

*The slope of this line is ~0, as indicated by the fact it appears horizontal. This indicates a lack of relationship between residuals and predictors.*

This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r plot of model residuals vs fitted values}
modelr::add_residuals(birthweight, fit) |>
  ggplot(aes(x = babysex, y = resid)) + geom_violin() +
  facet_wrap(.~frace)

modelr::add_residuals(birthweight, fit) |>
  ggplot(aes(x = gaweeks, y = resid)) + geom_violin() +
  facet_wrap(.~frace)
```

## Comparing to other models using CV

```{r}
cv_df =
  crossv_mc(birthweight, 80)  #80 cross validation runs

cv_df = 
  cv_df |> 
  mutate(
    fit  = map(.x = train, ~lm(bwt ~ ., data = .x)),
    fit2  = map(.x = train, ~lm(bwt~blength+gaweeks, data = .x)),
    fit3  = map(.x = train, ~lm(bwt~bhead*blength+bhead*babysex+blength*babysex, data = .x))) |>
  mutate(
    rmse_fit= map2_dbl(.x=fit, .y=test, ~rmse(model = .x, data = .y)),
    rmse_fit2= map2_dbl(.x=fit2, .y=test, ~rmse(model = .x, data = .y)),
    rmse_fit3 = map2_dbl(.x=fit3, .y=test, ~rmse(model = .x, data = .y)) 
  ) 
```


```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(
    model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

*Based on this graph displaying the RMSE of each model, I would conclude that the full model or model #3 with interaction terms have relatively similar RMSEs and are my top two choices for a model.*

